Technical Report

### 2024-02-20 Reports/tech_report1.tex

\subsection{Seek the best open ReLU number for layer 35 for normal 5x100}

@@

	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_17_21_56_00.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_17_21_56_00.b|. The first stores the gamma up to layer 3, and the second stores tests result of layer 5 in addition.
\end{itemize}

@@

>>>>

\subsection{Seek the best open ReLU number for layer 5 for normal 5x100}

@@

	\item \emph{Binary data}: \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_16_15_24_52.b| and \verb*|Diamond_record_6_100_dictionary_with_end_layer5_2024_02_16_15_24_52.b|. The first stores the gamma up to layer 3, and the second stores tests result of layer 5 in addition.
\end{itemize}

@@

\section{February 19 experiments}

\subsection{Randomly choose open ReLU for layer 5 for normal 5x100}

This experiment is to test the random open ReLU nodes for layer 5 normal 5x100 with new hyperplane constraints.

The running code's file name is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_random.py| (a copy for it is \verb*|DiamondLipschitz_all_layers_test_LP_use_bound_seek_open_number_random2.py|). And the partial output file name is \verb*|Gamma_5x100_normal_layer5_seek_openrelu_random.txt|.  It is based on the new hyperplane constraints, use MILP model to compute the gamma of layer 5 with different open ReLU numbers and nodes chosen randomly.

\begin{itemize}
	\item\emph{Experiments Id}: 021900102024

	\item\emph{Open $\ReLU$ number:} Open 17,20,23,26,29 ReLU nodes for each node, but choose open nodes randomly.

\begin{itemize}
	\item \emph{Log:} \verb*|Gamma_5x100_normal_layer5_seek_openrelu_random.txt| (from line 5776).

	\item \emph{Total time:} 11346.9s.

	\item \emph{Key results:} $\gamma$ for different open numbers are 1.1082117992614573    open 17
	1.0902650122404043     20
	1.0854613578404746     23
	1.0692115311756667     26
	1.055639230561528        29. This is much worse than open node by our method.
